Crowdy: Social Crowd Visualization

### 2011-04-29 docs/crowdy_gui.tex
Fixed final report and submitted to the Ship.

\subsubsection{How Might We Help}
Apart from the original Twitter interface that provides only a local view of
the most current tweets issued by each user's followee or some local trending
topics, our final system should be able to aggregate the data to find global,
regional, and local phenomenons. The final product is also adjustable that fit
into different expertise and purpose of usage based on the role of the users.

>>>>

\subsubsection{How Might We Help}
Apart from the original Twitter interface that provides only a local view of
the most current tweets issued by each user's friends or some local trending
topics, our final system should be able to aggregate the data to find global,
regional, and local phenomenons. The final product is also adjustable that fit
into different expertise and purpose of usage based on the role of the users.
